Formal Grammars as Functors and Formal Grammars as Types in Non-commutative Linear-Non-Linear Type Theory

### 2024-01-20 paper/paper.tex
comments

@@

To this end we define
\pedro{I'm pretty sure that these definitions have been somewhat presented
  in ``Glueing and orthogonality for models of linear logic'' by Hyland and Schalk.
We should probably cite them so that we don't have to rederive their constructions and proofs here.}
\begin{enumerate}
\item $(\phi, S) \otimes (\psi, T) = (\phi \otimes \psi, S\otimes T)$ where
  \[ (S \otimes T)(w, p) = (w_1w_2 = w) \times (q_1,q_2 = p) \times S\,w_1\,q_1 \times T\,w_2\,q_2\]
\item $(\phi, S) \multimap (\psi, T) = (\phi \multimap \psi, S \multimap T)$ where
  \[ (S \multimap T)(w,p) = w' \to q \to S\,w'\,q \to T (ww') (p\,q) \]
\item $\mu X. ??$ ??
\end{enumerate}

@@

To see this consider a case distinction on $e : NFA(g \oplus g')$. \steven{I could type out the equality proof term, but it blows up in size and doesn't seem like a useful way to capture this iso. I have a commented out version of it above. Going to refactor tomorrow to something more sane, as these as are the crux of the proofs of equality} \steven{In any case, the NFA-to-grammar direction of these isos should all follow from some $\eta$-rule on the structure of the type for the start state, right?} Without loss of generality assume that $e = \textbf{in}_{X_{s}'} u$. Then, $\mathsf{mfold}(e) = \textbf{in}_{g}(\phi^{-1}u)$ and passing this through the above case statement results in $\textbf{in}_{{X_{s}'}}(\phi(\phi^{{-1}}u)) = \textbf{in}_{{X_{s}'}}(u) = e$. Further,

@@

>>>>

\paragraph{Beyond Simple Types}

\begin{definition}
  A model is a locally Cartesian category equipped with an internal Kleene category.
\end{definition}

\begin{theorem}
  The presheaf category $\Set^{\cat{\Sigma^*}}$ is a model.
\end{theorem}

@@

To this end we define
\begin{enumerate}
\item $(\phi, S) \otimes (\psi, T) = (\phi \otimes \psi, S\otimes T)$ where
  \[ (S \otimes T)(w, p) = (w_1w_2 = w) \times (q_1,q_2 = p) \times S\,w_1\,q_1 \times T\,w_2\,q_2\]
\item $(\phi, S) \multimap (\psi, T) = (\phi \multimap \psi, S \multimap T)$ where
  \[ (S \multimap T)(w,p) = w' \to q \to S\,w'\,q \to T (ww') (p\,q) \]
\item $\mu X. ??$ ??
\end{enumerate}

@@

To see this consider a case distinction on $e : NFA(g \oplus g')$. \steven{I could type out the equality proof term, but it blows up in size and doesn't seem like a useful way to capture this iso. I have a commented out version of it above. Going to refactor tomorrow to something more sane, as these as are the crux of the proofs of equality} \steven{In any case, the NFA-to-grammar direction of these isos should all follow from some $\eta$-rule on the structure of the type for the start state, right?}
\pedro{What I like doing in these cases is either presenting the high-level structure of the proof, e.g., ``by applying the rules <...> we can conclude'', or present the full proof in the appendix.
  Since in this case it feels like it won't be a particularly illuminating proof, I suggest doing
the former.}
Without loss of generality assume that $e = \textbf{in}_{X_{s}'} u$. Then, $\mathsf{mfold}(e) = \textbf{in}_{g}(\phi^{-1}u)$ and passing this through the above case statement results in $\textbf{in}_{{X_{s}'}}(\phi(\phi^{{-1}}u)) = \textbf{in}_{{X_{s}'}}(u) = e$. Further,

@@

\pedro{I feel like that for the sake of organizing the paper, since the proof is non-trivial,
there should be a theorem environment with an accompanying proof environment}
